Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-06-16 Ben_Manuscripts/stochastic_transport/response_to_reviewers.tex

\section*{Response to Reviewer 1}

\begin{enumerate}[label={Comment \theenumi :}, leftmargin=3.9\parindent]

  \item \textit{\textbf{Page 5 line 19:} In this work, we use the output of our MD simulations
        to construct \textbf{two classes} of mathematical models which aim to predict membrane 
        performance while providing quantitative mechanistic insights. \\
        \textbf{Page 5 line 47:} We treat our system in terms of \textbf{two well-known} classes of 
        anomalous subdiffusion: \textbf{fractional Brownian motion} (FBM) subordinate to a 
        \textbf{continuous time random walk (CTRW)}, or subordinated FBM (sFBM) for short. \\ \\
        I am a little confused by these sentences, does the two well-known classes correspond to FBM
        and CTRW, or refer to different classes of modeling approaches used later in the manuscript?}

  %BJC: use a different word?
    %MRS: this is fine.

  Author reply: We thank the reviewer for identifying our potentially confusing choice of words.
  The first sentence (Page 5, line 19) refers more broadly to the two types of stochastic models 
  formulated in this work: the anomalous diffusion model and the Markov state-dependent dynamical
  %MRS: removed the capitalization on anomolous diffusion, not grammatical generally.
  model. The second quoted sentence (Page 5, line 47) refers to the different types of
  motion (FBM and CTRW) that give rise to anomalous diffusion specifically. The paragraph expands
  upon the introduction given in the previous paragraph. We have modified the second quoted 
  sentence as follows to remove ambiguity.

@@

  New text:
  \begin{quote}
  In this first approach, we treat our system in terms of two well-known types of molecular
  motion that leads to anomalous subdiffusion: 
  \end{quote}

  \item \textit{\textbf{MD-section} \\
        \textbf{Page 8 and 9} \\
        The authors refer to ref 13 (where these simulations have been performed before), 
        nevertheless I find that the MD section does not provide sufficient amount of details 
        to be self-contained. Could the authors specify the force field, as well as summarize 
        its reliability for this particular system (often simulations involving changed solutes
        through pores require polarizable force fields)?
   }

  Author reply: We thank the reviewer for pushing us to include more details about our 
  molecular simulations in order to boost reproducibility. The length of the manuscript made
  us wary to include information that could be accessed elsewhere, however there are 
  benefits to keep this very important section self-contained.

  New text:
  %MRS: add what tools used to parameterize them, like tleap, also that charges are AM1-BCC.
  %MRS: can mention that files are available in supporting information of previous paper, though
  %MRS: less relevant to this comment.
  \begin{quote}
  We parameterized monomers and solutes using the Generalized Amber Force Field (GAFF)~\cite{??} and
  water molecules using the TIP3P water model,~\cite{}
  %MRS: tweaked
  % We made each choice in order to
  % ensure that our approach is accessible and reproducible to a wide audience and so that
  %it is easy to study a broad range of solutes and monomer
  %chemistries in high throughput.
  GAFF is very commonly used in simulations with diverse organic chemical functionality, and was developed for consistency
  within the AMBER ecosystem, which used TIP3P as the water mode.
  We chose these standard force
  fields and generalizable parameterization approaches so that a range
  of solutes and monomers could self-consistently and easily be
  studied.  The main goal of this work is to develop stochastic models
  which can reproduce solute behavior on MD time scales, independent
  of the choice of force field. In future work, it may be beneficial
  to employ specialized force fields, including polarizable force
  fields or other higher-order effects in order to improve
  the accuracy of structure parameters and selectivity predictions.
  \end{quote}

  %BJC: not sure if anything should be added to text

  %MRS: generally, something should be added to the text for any
  %reviewer comment, even if just expanding what is already there to
  %include some of the points raised by the reviewers. It shows
  %good-faith efforts, and also if a reviewer has a concern, some
  %readers will have it as well, so might as well head it off.

  %BJC: I could use some help on justification
\item \textit{Next, reading this section I would 
        also like to know how well finite size effects are controlled for with this specific 
        membrane and these specific solutes.}

        %MRS: so I'm looking at
        %https://pubs.acs.org/doi/10.1021/jp0477147 and .  I think the
        %key point here is that most of the finite size corrections
        %have to do with the viscosity of the bath that the solute is
        %in.  I THINK that we can consider the viscosity essentially infinite, or at least
        %really really high, and therefore the corrections

        %MRS: also, I cut out the part about diffusing between pores,
        %but I don't think that's what they were getting at.

        %MRS: Do the solutes cross the boundary
        %conditions in the z direction much? You say they don't cross
        %between pores.  I don't think that's real point, though.

        We have not made any explicit finite size corrections, but
        they are less important for this work than for diffusion in
        other soft matter systems where diffusion is studied. In our
        previous work, we have shown that monomer diffusion is
        negligible on simulation time scales. Finite-size corrections
        to diffusion are primarily due to the hydrodynamics of the surroundings (cite two
        papers I sent), and the LLC membrane (outside of
        intramolecular motion and quasiharmonic vibration around it's
        average position) is therefore mostly motionless, with a very
        high effective viscosity.  This high surrounding viscosity
        should nearly eliminate these typical finite size effects.
        Additionally, we are usually comparing ratios of diffusion
        when we look at selectivity, and thus finite size effects
        should also mostly cancel out there.

        Verifying that there are indeed negligible finite size effects
        may be interesting in future work, but we do not feel it is
        justified for this study given the computational cost of
        studying larger systems. We also believe it would have little
        influence on the way in which we fit our models to the time
        series.

        %Our main focus is on the time series of the solutes in the
        %membrane pores. On the 5 $\mu s$ time scales which we
        %simulate, we do not observe any solutes that cross between
        %pores. Therefore, we expect similar solute behavior in larger
        %arrays of pores.

  %MRS: I think it's always good practice to have a text change
  %corresponding to every reviewer comment, even if it's just to
  %clarify.  This proves that MRS: we are taking the reviewer
  %seriously.

  To clarify this logic, we have added the following text:

  \begin{quote}
    Think about text here once we agree on the approach to response.
    \end{quote}

\item \textit{Lastly, it would be natural to report the size of the
  system in this section (I found it eventually in the introduction
  after searching for it throughout the manuscript).}

@@

\item \textit{Lastly, it would be natural to report the size of the
  system in this section (I found it eventually in the introduction
  after searching for it throughout the manuscript).}

  We added the following text in order to inform the reader of the system's size:

  New text:
  \begin{quote}
  %MRS: couldn't hurt to add cell dimensions  
  Each unit cell contains $\sim$ 62,000 total atoms. % BJC: do you think they want unit cell dimensions? X x Y x Z? 
  \end{quote}

@@

  \item \textit{\textbf{Figure 5 page 25:} \\
		First, the symbols within the figure are very small and barely readable, and probably not
		according to authors guidelines for figures. Second, the caption, as with the other captions of
		this manuscript, contain a lot of interpretation that normally are placed in the main text. This
		might be a particular style of the authors that has its benefits, however in this specific case the
		caption fails at explaining what exactly this figure is showing. The way I interpret this figure is:
		the symbol on the y-axis marks a general parameter and the boldface symbol marks the
		parameter shown in the histogram. Am I correct? If so, I would strongly recommend modifying
		y-axis and the caption to make this clear.}

		Author reply:

		We thank the reviewer for their constructive feedback. The fontsize in the figure is indeed too small.
		We have modified the plots in the figure to have larger, more readable font. We also took this 
		opportunity to increase the font size on Figures 6--8.

		The reviewer is correct in their interpretation of the figures. For clarity, we modified the y-axes as
		well as the caption in order to further aid the reader in reading them. We also made efforts to cut
                down on the interpretatio that is already presented in the main text.
                We made similar modifications to Figure 6 since it is an
		analogous figure. Our caption changes are presented below.

@@

        \begin{quote}

          The selectivity between pairs of species changes monotonically with
	      pore length. The strength of dependence on pore length depends on
	      the difference between $\beta$ values. 
		  %BJC: All of this is in the text.	      
	      \sout{The largest differences in solute
	      flux result in high selectivities at any pore length. This membrane
	      may be a good candidate for the separation of ethylene glycol from
	      acetic acid. Ethylene glycol has the lowest $\beta$ value while
	      acetic acid has the second highest, leading to strong length
	      dependence. Ethylene glycol also has the highest flux and acetic acid
	      has the lowest resulting in relatively high selectivities independent
	      of pore length.}

        \end{quote}

  \item \textit{\textbf{Page 6, line 55}: The second measure of success is based on the qualitative
        comparison between individual realizations of solute trajectories generated ...\\ \\
		Here I am a little curious. Are there no measures which can be used to quantify the similarity of
		the trajectories, such as autocorrelation functions etc, or are such measures inputs for the
		parametrization of the model which cannot be used?}

@@

		Author reply: In short, we do not believe there are any other suitable methods for comparing
		similarity beyond the checks which we show in this work. Autocorrelation is indeed an input 
		to the anomalous diffusion and Markov state-dependent dynamical model, specifically through
		the Hurst parameter which is generated by fitting to autocorrelation of solute jumps. The
		anomalous diffusion model is only parameterized by the distribution of hop length, the 
		distribution of dwell times and the degree of autocorrelation between hops, all of which
		are measured directly from MD. It may be possible to think of other metrics of success
		for the Markov state-dependent dynamical model, but it fails the qualitative test and
		thus does not merit any further checks.

  \item \textit{One question that came to mind reading the paper was: why is the model only in 
  		one dimension and not two (for example using cylindrical coordinates)?}

    %MRS: we probably want to phrase it a bit differently. I'm thinking you should you lead with the fact that it is quasi-2D, since radial information is built into having different states in the pores and the tails for the MSDDM and the 2-state anomalous diffusion models, then go into the other details.  Thoughts?

@@

		From a more mathematical standpoint, there are two factors which pose challenges with
		increasing dimensionality. First, we have a relatively low amount of data, and therefore
		it is challenging to adequately parameterize behavior as a continuous function of both 
		$r$ and $z$. Second, it is not trivial to simulate fractional motion in multiple dimensions.
		We were fortunate to find an efficient python implementation of FBM and we needed to
		develop our own approximation of 1D fractional L\'{e}vy motion based on literature. 
		We felt there was little to gain by models more complicated than those showcased in our
		work.

		However, we would like to acknowledge that we have a strong desire to incorporate data
		from multiple dimensions. We are actively investigating a new modeling approach which 
		allows us to overcome these issues and to use cylindrical representations with ease. %MRS: could cite the arXiv paperhere.

  \item \textit{\textbf{Page 35 line 12-14}: \\
   		We do not consider the two mode AD model because it has a broken correlation structure \\ \\
        I was a little disappointed to see only the single mode being used. Could the authors 
        elaborate on this point? Exactly how does this broken correlation structure hinder such
        an investigation?}

        Author reply: We are pleased with the reviewer's interest in the two-mode model. While it
        would be technically simple to apply the same mathematical framework to study the long time
        scale performance of the two-mode model, we feel it may be misleading to the reader.
        As described in the text, the predicted MSDs of the two-mode model may indeed show better 
        qualitative MSD behavior than the one-mode model. Specifically, the two-mode model becomes
        linear on long timescales which may be more consistent with our MD results. However, this 
        long time scale linear behavior of the two-mode model has
        %MRS: one  could argue that the fact the behavior is wrong means there's no mathematical basis - or the wrong mathematical basis, so simplifying.
        %only a mathematical basis and
        no physical basis.
        As discussed in the text, the one-mode model has persistent curvature
        since hop correlation persists indefinitely for fractional motion. However, for the two-mode
        model, each time a solute transitions between the pore and tail regions, we must generate a
        new FBM process because we lack a proven technique for simulating fractional 
        motion that incorporates time-dependent variation in the width of the hop length 
        distributions.

@@

        Perhaps, most importantly, Section 3.3 is primarily used to demonstrate our mathematical
        framework. Applying it to the two mode model would be trivial. We chose to use the one-mode 
        model for demonstration because it passes our qualitative and quantitative checks and is
        mathematically sound. As the reviewer points out, it is likely that our approach to 
        modeling the solute time series is not yet suitable to make quantitative predictions of 
        flux and selectivity. But our approach opens the door for applying the same analysis to 
        improved time series modeling techniques.

        To clarify this, we have modified the text
        \begin{quote}
          Text here:
          %MRS: Ben, choose where to put this.  It could be a simple one sentence modification or addition - you probably do explain why no 2-mode model, don't you?
        \end{quote}
  \item \textit{\textbf{Page 35 line 20-42:}\\
        A pore-length of 50 nm is a little underwhelming compared to 7 micrometers. Reading the paper
		I do not understand what lies behind this limitation - what hinders the sampling one really would
		like to have when doing such modeling? Also, you write about RAM-requirements scaling more
		than linearly (assuming with L). What exactly lies behind this scaling? Finally, just out of
		curiosity, are there ways of coarse-graining/renormalizing the random walk such that larger time
		and length scales can be reached? That being said, I am impressed by fit against the scaling
	  	law.}

@@

	  	Author reply: We can appreciate why the reviewer has questioned this limitation.
		When simulating fractional motion, each step must be correlated to all of its previous 
		steps. Therefore the computational cost increases with each added step. We show in the paper
		that the mean first passage time across the pores scales with L$^{\alpha}$, and $\alpha$ is
		always $\geq$ 2. As the degree of anti-correlation between hops increases, the scaling
		parameter also increases. Therefore, we need to generate very long trajectories, with 
		correlation between all data points, in order to sufficiently sample the MFPT distribution 
		before fitting them to Equation 9. This is especially challenging with slow-moving solutes
		like acetic acid. We needed to simulate over 2 million timesteps in order to sufficiently
		sample the MFPT over a 50 nm pore. This procedure becomes computationally expensive very
		quickly, and requires ample RAM to store the trajectories as they are constructed.

		Given the quality of our fits in Figure 11b, we felt it was not necessary to carry out the
		calculation for longer pores which would likely offer little extra benefit to the insight we
		already gained.

	  	This may be an issue that could be overcome by developing specialized algorithms and perhaps 
	  	by using a compiled computer language like C++.

	  	%BJC: Could reasonably go beyond 50 nm but 7 microns becomes tough
                %MRS: probably should explain that you COULD have gone beyond 50 nm, but there was no need, since it didn't improve the fit (if that is true).

	  	%BJC: building in the correlation structure is computationally expensive. Reference a paper describing how FBM is simulated
	  	%BJC: could benefit from optimized libraries, but python isn't fast enough
	  	%BJC: also need to specify the number of steps to take beforehand
	  	%BJC: truncated correlation functions may allow us to surpass the limitation

                %MRS: could also point out that we have come up with a
                %better approach along similar lines now (could cite arXiv paper), and so
                %continuing down this route is probably unnneeded.

@@

  \item \textit{In this paper the models are only evaluated by their ability of achieving 
		  self-consistency with the trajectories used as input. This is conceptually not ideal. 
		  Are there no experimental data or mathematical models which act as a reference for 
		  the models? Please elaborate.}

		  Author reply: The reviewer makes a valid point. This work started in parallel with experimental
		  work which promised solute flux and selectivities that we could compare directly to our
		  simulations. However, synthesizing an aligned hexagonal phase membrane has been a practical
		  challenge for our experimental collaborators and much of their focus has shifted to 
		  membranes formed by liquid crystals that self-assemble into bicontinuous cubic architectures
		  which are much simpler to synthesize. We have also started to shift our focus towards models 
		  of the bicontinuous cubic phase, which do have much more experiemntal data. However, our research
                  into generating physically accurate 
		  molecular models of that phase lags our work on time series modeling. In future work, we will
		  be able to apply this technique to these bicontinuous systems for which we have experimental data.

		  %BJC: I'm not sure this is worth bringing up

                  %MRS: probably should bring them up, since it allows you
                  %to respond to the question, and point out they are
                  %really insufficient because of he level of chemical
                  %detail.  Can just put them in the introduction
                  %describing the sort of model we want to move beyond.

		  As far as mathematical models, there are none that we know of to which we can reasonably
		  compare. Some work has been done to apply Donnan steric pore models to experimental data, 
		  but these models are continuum-based and have not been used in a predictive capacity.

@@

  \end{enumerate}

\noindent Optional comment to consider:\\
\begin{addmargin}[5.8em]{0em}
	\textit{Having read the paper thoroughly twice, I still struggle with the acronyms of the different random
	walks. Given that this is not a journal of stochastic processes, it is my opinion that the readability
	and accessibility of the manuscript would be greatly improved by writing the full names of the
	random walks in the text while keeping acronyms in figures. \\}

    %BJC: I'll address this once I incorporate things into the text.
    %MRS: yeah, we don't want people to have to read thoroughly twice.

@@

    Original text:

    \begin{quote}
    Mathematically modeling complex transport phenomena can be a powerful tool
    for extracting important physical information from molecular simulations. 
    In this study, we present two new approaches that use stochastic time series
    modeling to predict long time-scale behavior and macroscopic properties 
    from molecular simulation which can be generalized to other molecular systems
    where complex diffusion occurs. Specifically, we parameterize our models using
    long molecular dynamics (MD) simulation trajectories of a cross-linked 
    H\textsubscript{II} phase lyotropic liquid crystal (LLC) membrane in order to
    predict solute mean squared displacements (MSDs), solute flux, and
    solute selectivity in macroscopic length pores.    
    \end{quote}

	Modified text (highlighted in red):

	\begin{quote}
    %MRS: some suggested tweaks to describe the process more directly.
    \textcolor{red}{Using molecular simulations to fit mathematical models of complex transport phenomena
    that have more direct connection to experimental observables
    can be a powerful tool
    for extracting important physical information from these molecular simulations}. 
    In this study, we present two new approaches that use stochastic time series
    modeling to predict long time-scale behavior and macroscopic properties 
    from molecular simulation which can be generalized to other molecular systems
    where complex diffusion occurs. \textcolor{red}{In our previous work, we studied long 
    molecular dynamics (MD) simulation trajectories of a cross-linked 
    H\textsubscript{II} phase lyotropic liquid crystal (LLC) membrane where we
    observed subdiffusive solute transport behavior characterized by intermittent
    hops separated by periods of entrapment. In this work, we use our models to 
    parameterize the behavior of the same systems, so we can generate characteristic
    trajectory realizations that can be used} to predict solute mean squared 
    displacements (MSDs), solute flux, and solute selectivity in macroscopic length pores.
    \end{quote}

### 2020-07-12 Ben_Manuscripts/stochastic_transport/Final_Draft_JCTC.tex
added TOC graphic
Improvements to figure readability
Incorporated reviewer responses into main document

\usepackage{multirow}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
%\usepackage{caption}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{diagbox}
\usepackage{array}

@@

  Mathematically modeling complex transport phenomena can be a powerful tool
  for extracting important physical information from molecular simulations. 
  In this study, we present two new approaches that use stochastic time series
  modeling to predict long time-scale behavior and macroscopic properties 
  from molecular simulation which can be generalized to other molecular systems
  where complex diffusion occurs. Specifically, we parameterize our models using
  long molecular dynamics (MD) simulation trajectories of a cross-linked 
  H\textsubscript{II} phase lyotropic liquid crystal (LLC) membrane in order to
  predict solute mean squared displacements (MSDs), solute flux, and
  solute selectivity in macroscopic length pores.

@@

  We show that both stochastic models reasonably reproduce the MSDs calculated 
  from MD simulations. However, qualitative differences between MD and Markov 
  state dependent model-generated trajectories may in some cases limit their 
  usefulness. With these parameterized stochastic models, we demonstrate how 
  one can estimate flux of a solute across a macroscopic-length pore and, based
  on those quantities, the membrane's selectivity towards each solute. This
  work therefore helps to connect microscopic, chemically-dependent solute 
  motions that do not follow simple diffusive behavior with long time-scale 
  behavior, in an approach generalizable to many types of molecular systems 
  with complex dynamics.

@@

  There is a large disparity between the time scales accessible to atomistic 
  molecular dynamics (MD) simulations and experiment. The dynamics of molecules 
  over nanoseconds of simulation may tell a very different story than that 
  inferred by bulk measurements on the time-scale of seconds. Understanding 
  complex dynamical behavior on short time-scales and connecting them with much
  longer time-scales can provide fundamental insight which can be used for 
  atomic level design of materials. In this work, we pursue this connection 
  applied to highly selective aqueous filtration membranes and demonstrate how
  one can gain chemical intuition which serves both theoretical and experimental
  researchers.

@@

  Molecular modeling may make it possible to efficiently evaluate solute-specific
  separation membranes using the available chemical space of LLC monomers by 
  allowing researchers to understand their macroscopic behavior based on 
  microscopic, chemically-dependent solute motions. To date, only a limited 
  subset of H\textsubscript{II} phase-forming LLC monomers have been studied
  experimentally in membrane applications.~\cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, they have demonstrated selectivities that
  could not be explained beyond speculation and vague empirical
  correlations.~\cite{dischinger_application_2017} Atomistic molecular modeling
  can provide the resolution necessary to identify molecular interactions that
  are key to separation mechanisms, allowing us to move beyond Edisonian design
  approaches.

  In our previous work,~\cite{coscia_chemically_2019} we used molecular
  dynamics (MD) simulations to study the transport of 20 small polar molecules
  in an H\textsubscript{II} phase LLC membrane. 
  %We chose to study the
  %H\textsubscript{II} phase because it is a simpler geometry to model than the
  %Q\textsubscript{I} phase and significantly more structural data is available
  %to help ensure molecular models are consistent with experiment. 
  In general,
  we observed subdiffusive transport behavior characterized by intermittent
  hops separated by periods of entrapment. We identified three mechanisms
  responsible for the solute trapping behavior: entanglement among monomer
  tails, hydrogen bonding with monomer head groups, and association with the
  monomer's sodium counter ions.

  Up through our previous studies, our molecular models have provided valuable
  qualitative mechanistic insight with some quantitative support. This insight
  already allows us to speculate about new LLC monomer designs. However, they
  would be of greater value to a larger set of researchers if we could provide
  quantitative predictions of macroscopic observables such as solute flux and
  selectivity. Due to the size of the types of systems we are studying (at
  least 62,000 atoms) it is prohibitively expensive and time-consuming to run
  simulations longer than those performed for this work ($\sim$5 $\mu$s). Even
  with the relatively large size of our system, we only simulate 24 solute
  trajectories per unit cell in order to minimize solute-solute interactions.
  We are in need of an efficient method which can use our limited atomistic 
  simulation data sets in order to predict long timescale solute behavior.

@@

  In this work, we use the output of our MD simulations to construct two
  classes of mathematical models which aim to predict membrane performance
  while providing quantitative mechanistic insights. The functional forms of
  these models are driven by mechanistic observations from our previous work and
  their inputs are parameterized using a substantial amount of data generated
  by long ($\geq 5~\mu$s) MD simulations. Where sufficiently close to observed data,
  these fitted models provide a way to propagate information about solute 
  trajectories gathered at the microsecond time scale to realistic experimental 
  time scales.

  We constructed our first model by applying the existing rigorous theoretical
  foundation which describes the motion of particles that exhibit non-Brownian,
  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} 
  The tools introduced by fractional calculus are instrumental to this 
  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the normally
  linear diffusion equation to fractional derivative orders, providing descriptions
  of a much more diverse set of behavior, including subdiffusion, a type of 
  anomalous diffusion exhibited by solutes on the simulation time scales of this
  study.~\cite{klages_anomalous_2008}

  We treat our system in terms of two well-known classes of anomalous
  subdiffusion: fractional Brownian motion (FBM) subordinate to a 
  continuous time random walk (CTRW), or subordinated FBM (sFBM) for short. 
  FBM is common in crowded, viscoelastic environments where each jump comes 
  from a Gaussian distribution but is anti-correlated to its previous steps.
  ~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  A pure CTRW is characterized by a distribution of hop lengths and dwell times, 
  where trajectories consist of sequential independent random draws from each
  distribution.~\cite{montroll_random_1965} If the draws are not independent,
  then the hop sequence generation process can be described as subordinate to
  the CTRW. In our case, we observe anti-correlated draws from the hop distribution
  suggesting an FBM process is subordinate to the CTRW.

@@

  If one has knowledge of the primary mechanisms leading to anomalous diffusion
  behavior, one may gain additional insight by formulating a state-based model,
  such as Markov state models (MSMs). MSMs are a popular class of models used
  to project long timescale system properties based on molecular simulation
  trajectories by identifying different dynamical modes and quantifying the
  rates of transitions between them. MSMs are frequently used to study systems
  with slow dynamics, such as protein
  folding.~\cite{snow_how_2005,chodera_automatic_2007} Researchers typically
  aim to come up with a low dimensional representation of the system based on
  features which preserve the process kinetics. This still often results in
  hundreds to thousands of distinct states.~\cite{chodera_markov_2014}

  Our second modeling approach applies an extended MSM framework to a
  relatively small set of known states based on the three previously observed
  solute trapping mechanisms. Standard MSMs are typically applied to determine
  equilibrium populations of states and the kinetics of transitions between
  those states.~\cite{bowman_using_2009} We extend the framework to include
  state-dependent fluctuations and correlations in solute position. The model
  determines the magnitude of a solute's fluctuations from its average trapped
  position and the degree of correlation with previous fluctuations by its current
  state. To distinguish our approach from standard MSMs, we have named it the
  Markov state-dependent dynamical model (MSDDM).

>>>>

\usepackage{multirow}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
%\usepackage{caption}
\usepackage{amsmath} % or simply amstext
\usepackage{amssymb}
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{xr}
\usepackage{diagbox}
\usepackage{array}
\usepackage{upgreek}

@@

  % BJCR: r2_comment2 - replacement to following commented out paragraph  
  Using molecular simulations to fit mathematical models of complex transport phenomena
  that have more direct connection to experimental observables can be a powerful tool
  for extracting important physical information from these molecular simulations. 
  In this study, we present two new approaches that use stochastic time series modeling
  to predict long timescale behavior and macroscopic properties from molecular 
  simulation which can be generalized to other molecular systems where complex 
  diffusion occurs. In our previous work, we studied long molecular dynamics (MD) 
  simulation trajectories of a cross-linked H\textsubscript{II} phase lyotropic liquid
  crystal (LLC) membrane where we observed subdiffusive solute transport behavior 
  characterized by intermittent hops separated by periods of entrapment. In this work,
  we use our models to parameterize the behavior of the same systems, so we can generate
  characteristic trajectory realizations that can be used to predict solute mean squared 
  displacements, solute flux, and solute selectivity in macroscopic length pores.

%  Mathematically modeling complex transport phenomena can be a powerful tool
%  for extracting important physical information from molecular simulations. 
%  In this study, we present two new approaches that use stochastic time series
%  modeling to predict long timescale behavior and macroscopic properties 
%  from molecular simulation which can be generalized to other molecular systems
%  where complex diffusion occurs. Specifically, we parameterize our models using
%  long molecular dynamics (MD) simulation trajectories of a cross-linked 
%  H\textsubscript{II} phase lyotropic liquid crystal (LLC) membrane in order to
%  predict solute mean squared displacements (MSDs), solute flux, and
%  solute selectivity in macroscopic length pores.

@@

  We show that both stochastic models reasonably reproduce the MSDs calculated 
  from MD simulations. However, qualitative differences between MD and Markov 
  state dependent model-generated trajectories may in some cases limit their 
  usefulness. With these parameterized stochastic models, we demonstrate how 
  one can estimate flux of a solute across a macroscopic-length pore and, based
  on those quantities, the membrane's selectivity towards each solute. This
  work therefore helps to connect microscopic, chemically-dependent solute 
  motions that do not follow simple diffusive behavior with long timescale 
  behavior, in an approach generalizable to many types of molecular systems 
  with complex dynamics.

@@

  There is a large disparity between the timescales accessible to atomistic 
  molecular dynamics (MD) simulations and experiment. The dynamics of molecules 
  over nanoseconds of simulation may tell a very different story than that 
  inferred by bulk measurements on the timescale of seconds. Understanding 
  complex dynamical behavior on short timescales and connecting them with much
  longer timescales can provide fundamental insight which can be used for 
  atomic level design of materials. In this work, we pursue this connection 
  applied to highly selective aqueous filtration membranes and demonstrate how
  one can gain chemical intuition which serves both theoretical and experimental
  researchers.

@@

  Molecular modeling may make it possible to efficiently evaluate solute-specific
  separation membranes using the available chemical space of LLC monomers by 
  allowing researchers to understand their macroscopic behavior based on 
  microscopic, chemically-dependent solute motions. To date, only a limited 
  subset of H\textsubscript{II} phase-forming LLC monomers have been studied
  experimentally in membrane applications.~\cite{carter_glycerol-based_2012,hatakeyama_nanoporous_2010,smith_ordered_1997,zhou_assembly_2003,resel_structural_2000}
  Even within this small subset, they have demonstrated selectivities that
  could not be explained beyond speculation and vague empirical
  correlations.~\cite{dischinger_application_2017} 
  % r1_comment10 -new text  
  Some work has been done to apply
  Donnan steric pore models to experimental LLC membrane data, but these models 
  are continuum-based and are not effective as tools for explaining complex
  solute-membrane interactions.~\cite{hatakeyama_water_2011} 
  Atomistic molecular modeling can provide the 
  resolution necessary to identify molecular interactions that are key to separation
  mechanisms, allowing us to move beyond more traditional Edisonian design approaches.

  In our previous work,~\cite{coscia_chemically_2019} we used molecular
  dynamics (MD) simulations to study the transport of 20 small polar molecules
  in an H\textsubscript{II} phase LLC membrane. 
  %We chose to study the
  %H\textsubscript{II} phase because it is a simpler geometry to model than the
  %Q\textsubscript{I} phase and significantly more structural data is available
  %to help ensure molecular models are consistent with experiment. 
  In general,
  we observed subdiffusive transport behavior characterized by intermittent
  hops separated by periods of entrapment. 
  % We identified 
  % BJCR: r2_comment3 - modified to work in figure reference
  The complex membrane topology (see Figure~\ref{fig:membrane_structure}) gives rise
  to
  three mechanisms
  responsible for the solute trapping behavior: entanglement among monomer
  tails, hydrogen bonding with monomer head groups, and association with the
  monomer's sodium counter ions.

  Up through our previous studies, our molecular models have provided valuable
  qualitative mechanistic insight with some quantitative support. This insight
  already allows us to speculate about new LLC monomer designs. However, they
  would be of greater value to a larger set of researchers if we could provide
  quantitative predictions of macroscopic observables such as solute flux and
  selectivity. Due to the size of the types of systems we are studying (at
  least 62,000 atoms) it is prohibitively expensive and time-consuming to run
  simulations longer than those performed for this work ($\sim$5 $\upmu$s). Even
  with the relatively large size of our system, we only simulate 24 solute
  trajectories per unit cell in order to minimize solute-solute interactions.
  We are in need of an efficient method which can use our limited atomistic 
  simulation data sets in order to predict long timescale solute behavior.

@@

  In this work, we use the output of our MD simulations to construct two
  classes of mathematical models which aim to predict membrane performance
  while providing quantitative mechanistic insights. The functional forms of
  these models are driven by mechanistic observations from our previous work and
  their inputs are parameterized using a substantial amount of data generated
  by long ($\geq 5~\upmu$s) MD simulations. Where sufficiently close to observed data,
  these fitted models provide a way to propagate information about solute 
  trajectories gathered at the microsecond timescale to realistic experimental 
  timescales.

  We constructed our first model by applying the existing rigorous theoretical
  foundation which describes the motion of particles that exhibit non-Brownian,
  or anomalous, transport behavior.~\cite{metzler_random_2000,bouchaud_anomalous_1990} 
  The tools introduced by fractional calculus are instrumental to this 
  theory.~\cite{gorenflo_fractional_1997} They allow us to generalize the normally
  linear diffusion equation to fractional derivative orders, providing descriptions
  of a much more diverse set of behavior, including subdiffusion, a type of 
  anomalous diffusion exhibited by solutes on the simulation timescales of this
  study.~\cite{klages_anomalous_2008}

%  We treat our system in terms of two well-known classes of anomalous
%  subdiffusion: 
  \label{r1_comment1}  % BJCR: replaced first sentence
  In this first approach, we treat our system in terms of two well-known types
  of molecular motion which lead to anomalous subdiffusion:   
  fractional Brownian motion (FBM) subordinate to a 
  continuous time random walk (CTRW), or subordinated fractional Brownian motion
  (sFBM) for short. Fractional Brownian motion is common in crowded, viscoelastic 
  environments where each jump comes from a Gaussian distribution but is 
  anti-correlated to its previous steps.~\cite{mandelbrot_fractional_1968,jeon_fractional_2010,banks_anomalous_2005}
  A pure continuous time random walk is characterized by a distribution of hop 
  lengths and dwell times, where trajectories consist of sequential independent
  random draws from each distribution.~\cite{montroll_random_1965} If the draws
  are not independent, then the hop sequence generation process can be described 
  as subordinate to the continuous time random walk. In our case, we observe 
  anti-correlated draws from the hop distribution suggesting a subordinated 
  fractional motion process. % is subordinate to the continuous time random walk.

@@

  If one has knowledge of the primary mechanisms leading to anomalous diffusion
  behavior, one may gain additional insight by formulating a state-based model,
  such as a Markov state model. Markov state models are a popular class of models
  used to project long timescale system properties based on molecular simulation
  trajectories by identifying different dynamical modes and quantifying the
  rates of transitions between them. Markov state models are frequently used to
  study systems with slow dynamics, such as protein 
  folding.~\cite{snow_how_2005,chodera_automatic_2007} Researchers typically
  aim to come up with a low dimensional representation of the system based on
  features which preserve the process kinetics. This still often results in
  hundreds to thousands of distinct states.~\cite{chodera_markov_2014}

  Our second modeling approach applies an extended Markov state modeling 
  framework to a relatively small set of known states based on the three 
  previously observed solute trapping mechanisms. Standard Markov state models
  are typically applied to determine equilibrium populations of states and 
  the kinetics of transitions between those states.~\cite{bowman_using_2009}
  We extend the framework to include state-dependent fluctuations and 
  correlations in solute position. The model determines the magnitude of a 
  solute's fluctuations from its average trapped position and the degree of 
  correlation with previous fluctuations by its current state. To distinguish 
  our approach from standard Markov state models, we have named it the
  Markov state-dependent dynamical model (MSDDM).

  We determine the degree of success of our modeling approaches in two ways.
  First, if we can closely reproduce solute mean squared displacements
  measured from MD simulations with realizations of our models, then it is likely that the model
  sufficiently captures solute dynamics and can be used in a predictive
  capacity. Even if a model fails to reproduce the MD MSDs, there is value in
  uncovering the cause of the deviation. The second measure of success is based
  on the qualitative comparison between individual realizations of solute 
  trajectories generated by our models and those observed from MD simulations. 
  Even if we can reproduce the solute MSDs based on realizations of our models,
  the absence or inappropriate reproduction of hopping and trapping behavior may
  indicate underlying model issues.
